\documentclass{report}
\usepackage{indentfirst}
\usepackage[margin=2cm]{geometry}
\begin{document}
\section*{MarioAI Benchmark. Level Generator. Usage examples.}
Here are some examples how to use combination of various options. \\
Launch the benchmark as usual : \texttt{java~ch.idsia.scenarios.Main [params]}. \\ Short form is used further in the text: \texttt{Main -lco off}.
\begin{enumerate}
\item A flat level\footnote{Here and further option \emph{-le} used with key \emph{off} to disable creatures.}: \newline %1
\texttt{Main~-lco~off~-lb~off~-le~off~-lhb~off~-lg~off~-ltb~off~-lhs~off~-lc~off~-lde~off~-lf~on.}
\item A flat level with blocks:\newline %2
\texttt{Main~-lco~off~-lb~on~-le~off~-lhb~off~-lg~off~-ltb~off~-lhs~off~-lc~off~-lde~off~-lf~on.}
\item Blocks and coins:\newline %3
\texttt{Main~-lco~on~-lb~on~-le~off~-lhb~off~-lg~off~-ltb~off~-lhs~off~-lc~off~-lde~off.}
\item Blocks, creatures\footnote{Here and further option \emph{-le} used with key \emph{g,gw,gk,gkw,rk,rkw,s,sw} to enable creatures on the level.In this case selected creatures will be placed on the level regardless of the difficulty of the level.} and coins:\newline %4
\texttt{Main~-lco~on~-lb~on~-le~g,gw,gk,gkw,rk,rkw,s,sw~-lhb~off~-lg~off~-ltb~off~-lhs~off~-lc~off~-lde~off.}
\item Blocks, hidden blocks and coins:\newline %5
\texttt{Main~-lco~on~-lb~on~-le~0~-lhb~on~-lg~off~-ltb~off~-lhs~off~-lc~off~-lde~off.}
\item Blocks, hidden blocks, coins and creatures:\newline %6
\texttt{Main~-lco~on~-lb~on~-le~g,gw,gk,gkw,rk,rkw,s,sw~-lhb~on~-lg~off~-ltb~off~-lhs~off~-lc~off~-lde~off.}
\item Deadends  and blocks:\newline %7
\texttt{Main~-lco~off~-lb~on~-le~off~-lhb~off~-lg~off~-ltb~off~-lhs~off~-lc~off~-lde~on.}
\item Deadends, blocks and hidden blocks:\newline %8
\texttt{Main~-lco~off~-lb~on~-le~off~-lhb~on~-lg~off~-ltb~off~-lhs~off~-lc~off~-lde~on.}
\item Deadends and hidden blocks:\newline %9
\texttt{Main~-lco~off~-lb~off~-le~off~-lhb~on~-lg~off~-ltb~off~-lhs~off~-lc~off~-lde~on.}
\item Deadends, blocks, hidden blocks and creatures:\newline %10
\texttt{Main~-lco~off~-lb~on~-le~g,gw,gk,gkw,rk,rkw,s,sw~-lhb~on~-lg~off~-ltb~off~-lhs~off~-lc~off~-lde~on.}
\item A flat level with tubes: \newline %11
\texttt{Main~-lco~off~-lb~off~-le~off~-lhb~off~-lg~off~-ltb~on~-lhs~off~-lc~off~-lde~off~-lf~on.}
\item A flat level with gaps: \newline %12
\texttt{Main~-lco~off~-lb~off~-le~off~-lhb~off~-lg~on~-ltb~off~-lhs~off~-lc~off~-lde~off~-lf~on.}
\item Tubes and gaps: \newline %13
\texttt{Main~-lco~off~-lb~off~-le~off~-lhb~off~-lg~on~-ltb~on~-lhs~off~-lc~off~-lde~off.}
\item Cannons: \newline %14
\texttt{Main~-lco~off~-lb~off~-le~off~-lhb~off~-lg~off~-ltb~off~-lhs~off~-lc~on~-lde~off.}
\item Tubes, gaps and cannons: \newline %15
\texttt{Main~-lco~off~-lb~off~-le~off~-lhb~off~-lg~on~-ltb~on~-lhs~off~-lc~on~-lde~off.}
\item Goomba and winged spiky\footnote{here and further option \emph{-le} used with different key(e.g. g,sw). In this case selected creatures will be placed on the level regardless of the difficulty of the level.}: \newline %16
\texttt{Main ~-lco~off~-lb~off~-le~g,ws~-lhb~off~-lg~off~-ltb~off~-lhs~off~-lc~off~-lde~off.}
\item Deadends and red koopa: \newline %17
\texttt{Main~-lco~off~-lb~off~-le~rk~-lhb~off~-lg~off~-ltb~off~-lhs~off~-lc~off~-lde~on.}
\item Mario gravity: \newline %18
\texttt{Main~-mgr~1.4.}
\item Mario gravity and creatures gravity: \newline %19
\texttt{Main~-mgr~1.4~-cgr~0.8.}


\end{enumerate}
\end{document}